Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-04 RR_manuscript/Draft_RR.tex
include paragraph on funnel plots in section 2.4.2

\hypertarget{methods-mostly-copy-paste-from-evo-rr}{%
\section{Methods (mostly copy-paste from Evo-RR)}\label{methods-mostly-copy-paste-from-evo-rr}}

@@

@@

\begin{itemize}
\tightlist
\item
  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model.
\item
  \emph{Measure of conservativeness} of the model specification.
\item
  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out.
\item
  \emph{Number of models} the teams will report to have run.
\item
  \emph{Major dimension} that has been measured to answer the research question.
\item
  \emph{Temporal window} that the measurement is taken over.
\item
  \emph{Demographic factors} of analysis teams and analysts.
\end{itemize}

@@

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).
The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: segment, syllable, word, phrase.

@@

\begin{itemize}
\tightlist
\item
  \ldots{}
\end{itemize}

@@

@@

@@

>>>>

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
This will be achieved through inspection of funnel plots (Light \& Pillemer, 1984; for a review see Egger, Smith, Schneider, \& Minder, 1997; and Sterne, Becker, \& Egger, 2005; for a critique Lau, Ioannidis, Terrin, Schmid, \& Olkin, 2006).
In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the \emph{x}-axis and estimated error (i.e.~standard deviation) on \emph{y}-axis.
In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \ref{fig:funnel-plot}).
A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.

\begin{figure}
\centering
\includegraphics{Draft_RR_files/figure-latex/funnel-plot-1.pdf}
\caption{\label{fig:funnel-plot}Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes. The vertical dashed line represents the meta-analitical mean.}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model.
\item
  \emph{Measure of conservativeness} of the model specification.
\item
  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out.
\item
  \emph{Number of models} the teams will report to have run.
\item
  \emph{Major dimension} that has been measured to answer the research question.
\item
  \emph{Temporal window} that the measurement is taken over.
\item
  \emph{Data exclusion}, whether data has been excluded or not.
\item
  \emph{Demographic factors} of analysis teams and analysts.
\end{itemize}

@@

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).

The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: segment, syllable, word, phrase.

@@

\begin{itemize}
\tightlist
\item
  \emph{Research experience} as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
\item
  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.
\end{itemize}

@@

\leavevmode\hypertarget{ref-egger1997}{}%
Egger, M., Smith, G. D., Schneider, M., \& Minder, C. (1997). Bias in meta-analysis detected by a simple, graphical test. \emph{British Medical Journal}, \emph{315}, 629--634.

@@

\leavevmode\hypertarget{ref-lau2006}{}%
Lau, J., Ioannidis, J. P. A., Terrin, N., Schmid, C. H., \& Olkin, I. (2006). The case of the misleading funnel plot. \emph{British Medical Journal}, \emph{333}(7568), 597--600.

\leavevmode\hypertarget{ref-light1984}{}%
Light, R. J., \& Pillemer, D. B. (1984). \emph{Summing up; the science of reviewing research}. Cambridge, MA (USA) Harvard Univ. Press.

@@

\leavevmode\hypertarget{ref-sterne2005}{}%
Sterne, J. A. C., Becker, B. J., \& Egger, M. (2005). The funnel plot. In H. R. Rothstein, A. J. Sutton, \& M. Borenstein (Eds.), \emph{Publication bias in meta-analysis: Prevention, assessment and adjustments} (pp. 75--98). Wiley Online Library.
